Legends for supplementary material

### 2019-05-28 Manuscript/Figures/figure_legends.Rmd
rearranged figures
editted legends

**Figure 1. Model Construction.** An illustration of the proposed model construction given cell line-specific Hi-C matrices. The contact matrix above is a visualization of the interconnectivity of chromosome 14 at 100 kb resolution, for the GM12878 cell line, on the intervals from 20 mb to 100 mb [@durand2016juicer]. The boundary coordinates of topologically association domains (TADs) were identified using the Arrowhead algorithm. To account for the uncertainty in TAD boundary detection, each boundary point was flanked on both sides by resolution-specific genomic regions (bins). The response vector $Y$, used for classification, was determined by whether a genomic bin overlapped with a flanked boundary region (Y=1) or not (Y=0). The spatial relationship between positional coordinates of various functional genomic annotations, obtained from ENCODE, and the genomic bins were then used to define the feature space of the models.

**Figure 2. Ensemble Framework.** A diagram of the ensemble framework detailing the various combination of inputs used in the model building pipeline. A given system within the ensemble framework included the total number of genomic bins, labeled as having been overlapped with a flanked TAD boundary or not, as well as a feature space composed of 1 of 3 different predictor-type specific annotations. The data was then split into a 7:3 training:testing set ratio. A re-sampling technique was applied to the training set, followed by an elastic-net regularization to reduce the feature space. Lastly, a random forest classification model was performed on the re-sampled and reduced training set and validated on the held out testing set common to all ensemble systems in the framework.

**Figure 3. The three predictor types.** Three separate types of predictors were considered when quantifying the association between TAD boundaries and genomic annotations. Each predictor type was used to build the feature space of specific models in the ensemble framework. The _overlap count_ (OC) predictors consider the total number of genomic features that overlapped with each genomic bin. The _overlap percent_ (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin by the total bin width. The _distance_ ($log_{2}$ transformed) predictors were calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest genomic feature. [???should I include ABC here?]

@@

>>>>

**Figure 1. Ensemble Framework.** A diagram of the cell line specific ensemble framework detailing the various combination of inputs used in the model building pipeline. The minoirty and majority classes were represented by the genomic bins that overlapped with flanked TAD boundaries or did not, respectively. Functional genomic annotations obtained from the UCSC Genome Browser Database composed the feature space. The data was split into a 7:3 training to testing set ratio. A feature engineering step was included to isolate the spatial relationship, of increasing granularity, between annotations and genomic bins. Data re-sampling and regularization was applied to the training data. Lastly, a random forest classification algorithm was implemeted and validated on the testing data.

<!--
A given system within the ensemble framework included the total number of genomic bins, labeled as having been overlapped with a flanked TAD boundary ($Y=1$) or not ($Y=0$). The data matrix that composed the feature space was composed of predictor-type specific annotations represented by $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations. The data was then split into a 7:3 training to testing set ratio. A re-sampling technique was applied to the training set, followed by an elastic-net regularization to reduce the feature space. Lastly, a random forest classification model was performed on the re-sampled and reduced training set and validated on the held out testing set common to all ensemble systems in the framework.
-->

**Figure 2. Model Construction.** An illustration of the proposed model construction given cell line specific Hi-C matrices. The contact matrix above is a visualization of the interconnectivity of chromosome 14 at 100 kb resolution, for the GM12878 cell line, on the intervals from 20 mb to 100 mb [@durand2016juicer]. The boundary coordinates of topologically association domains (TADs) were identified using the Arrowhead algorithm. To account for the uncertainty in TAD boundary detection, each boundary point was flanked on both sides by resolution-specific genomic regions (bins). The response vector $Y$, used for classification, was determined by whether a genomic bin overlapped with a flanked boundary region ($Y=1$) or not ($Y=0$). The spatial relationship between positional coordinates of various functional genomic annotations, obtained from ENCODE, together with the genomic bins were then used to define the feature space of the models represented by the data matrix $X = \{X_1, X_2, ..., X_p\}$, where $p$ was the complete set of functional annotations.

**Figure 3. The three predictor types.** Three separate types of predictors were considered when quantifying the association between TAD boundaries and genomic annotations. Each predictor type was used to build the feature space of specific models in the ensemble framework. The _overlap count_ (OC) predictors consider the total number of genomic features that overlapped with each genomic bin. The _overlap percent_ (OP) predictors were calculated by dividing the sum of all feature widths within each specific bin by the total bin width. The _distance_ ($log_{2}$ transformed) predictors were calculated by measuring the distance (in bases) from the center of each genomic bin to the center of the nearest genomic feature.

@@

**Figure 8. Comparing $log_{2}$ distance profiles.** Boxplots illustrating the distribution of distances around 10 kb regions on the GM12878 genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential TFBS including SMC3, CTCF, RAD21, ZNF143, and YY1sc281. P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [**** = p < 0.00001].

### 2019-05-28 Manuscript/Supplementary/supplementary_legends.Rmd
editted legends

>>>>

**Figure 9. Comparing $log_{2}$ distance profiles.** Boxplots illustrating the distribution of distances around (A) 25 kb, (B) 50 kb, and (C) 100 kb regions on the GM12878 genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential TFBS including SMC3, CTCF, RAD21, ZNF143, and YY1sc281. P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [**** = p < 0.00001].

**Figure 10. Comparing $log_{2}$ distance profiles.** Boxplots illustrating the distribution of distances around (A) 10 kb, (B) 25 kb, (C) 50 kb, (D) 100 kb regions on the GM12878 genome that either overlapped with a flanked TAD boundary (Yes) or did not (No), for the most influential TFBS including SMC3, CTCF, RAD21, and ZNF143. P-values obtained from Wilcoxon Rank Sum tests are provided assessing the significance [**** = p < 0.00001].
